Missing data: a simple introduction

### 2020-03-03 Draft1.tex
Finished defining congeniality and added Rubin's rules

	\subsection{Congeniality: when the imputer's and analysts models differ}
	As mentioned in the introduction, modern data analysis' multiple phases mean that the assumptions underlying each phase and the relationship between the phases is an important object of study. Meng's [meng 1994] concept of congeniality provides a theoretical framework from which to evaluate these differences.

@@

@@

	Under congeniality, Rubin's rules for calculating standard errors, parameter values, and variance suffice.

>>>>

	\subsection{Congeniality: when the imputer's and analysts models differ}
	As mentioned in the introduction, modern data analysis' multiple phases mean that the assumptions underlying each phase and the relationship between the phases is an important object of study. Meng's [meng 1994] concept of congeniality provides a theoretical framework from which to evaluate these differences and most of this section is derived from his paper.

@@

	Additionally, let $g(Y^{m}|{Y^{o}, M}, A)$ be the imputation model, where A represents possible additional data the imputer has access to. Meng continues by stating ''The analysis procedure $P$ is said to be congenial to the imputation model $g(Y^{m}|{Y^{o}, M}, A)$ if one can find an f such that 1) f is congenial to $P$ and 2) the posterior predictive density for $Y^{m}$ derivd under f is identical to the imputation model $$f(Y{m}|{Y^{o}, M}) = g(Y{m}|{Y^{o}, M}, A) \forall Y^{m}$$

	Therefore if no such congenial f exists, then$P$ is said to be uncongenial to g. Notice that congeniality is defined with respect to a particular analysis procedure, meaning that an analyst can perform two types of analyses where one is congenial and the other is not. There are three main scenarios in which uncongeniality occurs in the context of missing data and MI. The first is when the imputation model is largely unknown to the analyst, often the case with public databases. Second is when the different needs of imputation and analysis require different models. Third is when one is conducting sensitivity analysis, which necessarily requires the testing of different models, some of which will be uncongenial.

@@

	At step 2) of MI, we have M sets of parameter estimates and their variances $\hat{\theta}_{i},\hat{Var_{i}} \qquad i=0,...,M$. The next step is to combine these into a single estimate. Under congeniality Rubin's combining rules suffice for giving us statistically valid estimates. The parameter estimate is simply the average $$\bar{\theta} = \frac{1}{M}\sum_{i=0}^{M}\hat{\theta}_{i}$$ and the variance associated with $\bar{\theta}$ is given by $$T = \bar{Var}+(1+\frac{1}{M}B)$$ where $$\bar{Var} = \frac{1}{M}\sum_{i=0}^{M}\hat{Var}_{i}$$ measures the within imputation variability and $$B = \frac{1}{M-1}\sum_{i=0}^{M}(\hat{\theta_{i}}-\bar{\theta})(\hat{\theta_{i}}-\bar{\theta})^{T}$$ measures the between imputation variability. The adjustment $(1+\frac{1}{M})$ is due to the finite number of imputations. If we let $M\rightarrow\infty$ then...
